Viscous Transport in Eroding Porous Media

### 2019-05-01 docs/transport/erosion_transport.tex
doing tranposrt paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Velocity}
The Stokes double-layer potential can be written as
\begin{align}
  \DDD[\eeta](\xx) &= 
    \frac{1}{2\pi} \int_{\Gamma} 
      \frac{\nn}{\rho^2} (\rr \cdot \eeta) ds_\yy + 
    \frac{1}{2\pi} \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta)ds_\yy \\
    &- \frac{1}{2\pi} x_1 \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) ds_\yy -
    \frac{1}{2\pi} x_2 \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) ds_\yy,
\end{align}
and this formulation is convenient since each of the integrals can be
written as a Laplacian double-layer potential,
\begin{align}
  \DD[\tau](\xx) = -\frac{1}{2\pi} \int_{\Gamma} \pderiv{}{\nn_\yy}
    \log(\rho) \tau(\yy) ds_\yy.
\end{align}
Finally, by identifying $\RR^2$ with $\CC$, for purely real $\tau$, the
Laplacian double-layer potential can be written as the real part of a
Cauchy integral
\begin{align}
  \DD[\tau](x) = \Re (v(x)),
  \qquad \text{where} \qquad
  v(x) = \frac{1}{2\pi i} \int_\Gamma \frac{\tau(y)}{x - y} dy.
\end{align}
Therefore, the Stokes double-layer potential can be written as five
Cauchy integrals and their derivatives with the density functions $\yy
\cdot \nn$, $\eta_1$, and $\eta_2.$

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Shear Stress}
Since the rate of erosion is proportional to the shear stress, we also
require the gradient of the Stokes double-layer potential $\nabla
\DDD[\eeta](\xx)$.  Using the Cauchy integral formulation, the gradient
of of the double-layer potential velocity is
\begin{align}
  \nabla\D[\eeta](\xx) = \frac{1}{2\pi}\nabla\int_{\Gamma}
    &\frac{\nn}{\rho^2}(\rr \cdot \eeta)ds_\yy +
  \frac{1}{2\pi}\nabla\nabla\int_{\Gamma}
    \frac{\rr \cdot \nn}{\rho^2}({\yy} \cdot\eeta) ds_y \\
  &- \frac{1}{2\pi} \nabla x_1 \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) ds_\yy -
  \frac{1}{2\pi} \nabla x_2 \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) ds_\yy.
\end{align}
Then, the deformation tensor can be written in terms of Cauchy integrals
\todo[inline]{For S-H to fill in}
\begin{align}
  \ssigma = \frac{1}{2} 
    \left(\nabla \DDD[\eeta] + \nabla^T \DDD[\eeta] \right) 
      \nn \cdot \ss = \ldots
\end{align}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Velocity}
The Stokes double-layer potential can be written as
\begin{align}
  \DDD[\eeta](\xx) &= 
    \frac{1}{2\pi} \int_{\Gamma} 
      \frac{\nn}{\rho^2} (\rr \cdot \eeta) ds_\yy + 
    \frac{1}{2\pi} \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta)ds_\yy \\
    &- \frac{1}{2\pi} x_1 \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) ds_\yy -
    \frac{1}{2\pi} x_2 \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) ds_\yy,
\end{align}
and this formulation is convenient since each of the integrals can be
written as a Laplacian double-layer potential,
\begin{align}
  \DD[\tau](\xx) = -\frac{1}{2\pi} \int_{\Gamma} \pderiv{}{\nn_\yy}
    \log(\rho) \tau(\yy) ds_\yy.
\end{align}
Finally, by identifying $\RR^2$ with $\CC$, for purely real $\tau$, the
Laplacian double-layer potential can be written as the real part of a
Cauchy integral
\begin{align}
  \DD[\tau](x) = \Re (v(x)),
  \qquad \text{where} \qquad
  v(x) = \frac{1}{2\pi i} \int_\Gamma \frac{\tau(y)}{x - y} dy.
\end{align}
Therefore, the Stokes double-layer potential can be written as five
Cauchy integrals and their derivatives with the density functions $\yy
\cdot {\color{red}\eeta}$, $\eta_1$, and $\eta_2,$
{\color{red}
\begin{align}
 u_1(\xx)&= \Re (v[\tau_1](x)) + \Re (v'[\yy\cdot\eeta](x)) 
           -x_1\Re (v'[\eta_1](x)) -x_2\Re (v'[\eta_2](x)),\\
 u_2(\xx)&= \Re (v[\tau_2](x)) - \operatorname{Im} (v'[\yy\cdot\eeta](x)) 
       +x_1\operatorname{Im} (v'[\eta_1](x)) 
      +x_2\operatorname{Im} (v'[\eta_2](x)),
\end{align}
where
\begin{align*} 
\DD[\eeta](\xx)=(u_1(\xx),u_2(\xx)), \,\, 
\xx=x_1+x_2, \,\,
\tau_1=(\eta_1+i\eta_2)\frac{\Re \, n}{n}, \text{ and }
\tau_2=(\eta_1+i\eta_2)\frac{\operatorname{Im} n}{n}.
\end{align*}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Shear Stress}
Since the rate of erosion is proportional to the shear stress, we also
require the gradient of the Stokes double-layer potential $\nabla
\DDD[\eeta](\xx)$.  Using the Cauchy integral formulation, the gradient
of of the double-layer potential velocity is
{\color{red}
\begin{align}
 \nabla\D[\eeta] (\xx)=
\left[
\begin{matrix}
\displaystyle\frac{\partial u_1(\xx)}{x_1} & \displaystyle\frac{\partial u_1(\xx)}{x_2}\\ \\
\displaystyle\frac{\partial u_2(\xx)}{x_1} & \displaystyle\frac{\partial u_2(\xx)}{x_2}
\end{matrix}
\right],
\end{align}
where 
\begin{align}
\frac{\partial u_1(\xx)}{x_1}&= \Re (v'[\tau_1](x)) + \Re (v''[\yy\cdot\eeta](x)) 
           -\Re (v'[\eta_1](x)) -x_1\Re (v''[\eta_1](x))-x_2\Re (v''[\eta_2](x)),\\
\frac{\partial u_1(\xx)}{x_2}&= - \operatorname{Im} (v'[\tau_1](x)) 
      - \operatorname{Im} (v''[\yy\cdot\eeta](x)) 
       +x_1\operatorname{Im} (v''[\eta_1](x)) 
       -\Re (v'[\eta_2](x))
      +x_2\operatorname{Im} (v''[\eta_2](x)),\\
\frac{\partial v_1(\xx)}{x_1}&= \Re (v'[\tau_2](x)) 
      -\operatorname{Im} (v''[\yy\cdot\eeta](x)) 
       +\operatorname{Im} (v'[\eta_1](x))
       +x_1\operatorname{Im} (v''[\eta_1](x)) 
      +x_2\operatorname{Im} (v''[\eta_2](x)),\\
\frac{\partial v_2(\xx)}{x_2}&= -\operatorname{Im} (v'[\tau_2](x)) 
      -\Re (v''[\yy\cdot\eeta](x)) 
       +x_1\Re (v''[\eta_1](x)) 
      +\operatorname{Im} (v'[\eta_2](x)
      +x_2\operatorname{Im} (v''[\eta_2](x)).
\end{align}
}
%\begin{align}
%  \nabla\D[\eeta](\xx) = \frac{1}{2\pi}\nabla\int_{\Gamma}
%    &\frac{\nn}{\rho^2}(\rr \cdot \eeta)ds_\yy +
%  \frac{1}{2\pi}\nabla\nabla\int_{\Gamma}
%    \frac{\rr \cdot \nn}{\rho^2}({\yy} \cdot\eeta) ds_y \\
%  &- \frac{1}{2\pi} \nabla x_1 \nabla \int_{\Gamma}
%      \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) ds_\yy -
%  \frac{1}{2\pi} \nabla x_2 \nabla \int_{\Gamma}
%      \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) ds_\yy.
Then, the deformation tensor can be written in terms of Cauchy integrals
\todo[inline]{For S-H to fill in}
\begin{align}
  \ssigma = \frac{1}{2} 
    \left(\nabla \DDD[\eeta] + \nabla^T \DDD[\eeta] \right) 
      \nn \cdot \ss = \ldots
\end{align}
